People

### 2025-07-20 people.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.
Update 'People' section in people.qmd to relocate Yeshwanth Cherapanamjeri's entry
Moved Yeshwanth Cherapanamjeri's listing from the current post-docs section to the form

@@

- Corine Elliot (2024) - Statistical Scientist, Berry Consultants
- James Duncan (2024) - Climate ML Engineering, Allen Institute for AI (AI2)
- Tiffany Tang (2023) - Clare Boothe Luce Assistant Professor, University of Notre Dame
- Yeshwanth Cherapanamjeri (2023) - Postdoctoral Researcher, MIT
- Dennis Shen (2023) - Assistant Professor, USC
- Spencer Frei (2023) - Assistant Professor, UC Davis
- Rebecca L. Barter (2022) - Research Assistant Professor, University of Utah
- Luiz Chamon (2022) - Research Group Leader, University of Stuttgart
- Angela Zhou (2022) - Assistant Professor, University of Southern California
- Briton Park (2022) - Citadel Securities
- Chandan Singh (2022) - Microsoft Research
- Keyan Nasseri (2022) - Google
- Wooseok Ha (2022) - AWS
- Yan Shuo Tan (2022) - Assistant Profressor, Department of Statistics and Data Science, National University of Singapore
- Xiao Li (2021) - Voleon
- Raaz Dwivedi (2021) - Postdoctoral scholar, MIT / Harvard
- Yu Wang (2020) - Two Sigma
- Merle Behr (2020) - Scientific Expert, Bayer AG
- Nicholas Altieri (2020) - Genentech
- Yuansi Chen (2019) - Assistant Professor, Department of Statistical Sciences, Duke University
- Karl Kumbier (2019) - Postdoctoral Researcher, UC San Francisco
- Jamie Murdoch (2019) - Co-founder / President, clientelligent.ai
- Soren Kunzel (2019) - Data Scientist, Citadel
- Simon Walter (2019) - Data Scientist, Bridgewater
- Sujayam Saha (2018) - Data Scientist, Google
- Reza Abbasi-Asl (2018) - Scientist, Allen Institute for Brain Science
- Christine Kuang (2017) - Data Scientist, Facebook
- Hanzhong Liu (2016) - Assistant Professor, Department of Statistics, Tsinghua University
- Sumanta Basu (2016) - Assistant Professor, Department of Statistics, Cornell University
- Sivaraman Balakrishnan (2016) - Assistant Professor, Department of Statistics, Carnegie Mellon University
- Adam Bloniarz (2016) - Data Scientist, Google
- Siqi Wu (2016) - Data Scientist, Citadel
- Hongwei Li (2015) - Senior Data Scientist, UBER
- Antony Joseph (2014) - Staff Data Scientist, Walmart eCommerce
- Taesup Moon (2013) - Research Staff Member, Samsung Advanced Institute of Technology
- Yuval Benjamini (2013) - Stein fellow, Statistics department, Stanford University
- Julien Mairal (2012) - Research Scientist, INRIA
- Yueqing Wang (2012) - Research Scientist, Google
- Hau-tieng Wu (2012) - Assistant Professor, Mathematics Department, University of Toronto
- Garvesh Raskutti (2012) - Assistant Professor, Department of Statistics, Univ. Wisconsin-Madison
- Luke W. Miratrix (2012) - Assistant Professor, Department of Statistics, Harvard University
- Harry Kim (2011) - Product Marketing Manager, Google
- Chinghway Lim (2011) - Assistant Professor, Department of Statistics and Applied Probability, National University of Singapore
- Karl Rohe (2011) - Assistant Professor, Department, University of Wisconsin-Madison.
- Kyle Jia (2010) - Assistant Professor, Peking University, China.
- David Purdy (2009) - Data Scientist, Uber
- Pradeep Ravikumar (2009) - Associate Professor, Department of Computer Sciences, University of Texas, Austin.
- Vince Vu (2009) - Assistant Professor, Department of Statistics, The Ohio State University
- Ethan Anderes (2008) - Assistant Professor, Department of Statistics, University of California, Davis
- Guilherme Rocha (2008) - Assistant Professor, Department of Statistics, Indiana University, Bloomington
- Peng Zhao (2006) - CEO of Citadel Securities, Citadel Investment Group in Chicago, IL.
- Nicolai Meinshausen (2006) - Professor, Department of Statistics, ETH Zurich
- Tao Shi (2005) - Quantitative Researcher, Citadel Investment Group in Chicago, IL.
- Gang Liang (2004) - Quantitative Operations Associate, Bank of America
- Rebecka Jörnsten (2000) - Associate Professor, Mathematical Statistics, Chalmers University of Technology
- Grace Chang (2000) - Senior Manager of Product Development, Marketing Dept, MTN Irancell

@@

- Arman Sabbaghi (2022)
- Yanjun Qi (2020)
- Ezequiel Smucler (2020)
- Laura Reiger (2019)
- Yanyan Lan (2018)
- Yahong Han (2016)
- Thibault Vatter
- Guoqiang Cai
- Trine Abrahamsen
- Xiaoling Lu
- Xiusheng Lu (2014)
- Xiangyu Chang (2012)
- Ling Hong (2012)
- Toshiyasu Matsushima (2012)
- Yanfeng Gu (2012) - Professor of Electronics Engineering, Harbin Institute of Technology
- Hai Zhang (2012)
- Rodolphe Jenatton (2010)
- Kenichi Hayashi (2010)
- Yangbo He (2010)
- Fei Wu (2010)
- Kei Kobayashi (2008)
- Xing Wang (2007)

>>>>

# People

@@

- Corine Elliot (2024) - Statistical Scientist, Berry Consultants
- James Duncan (2024) - Climate ML Engineering, Allen Institute for AI (AI2)
- Tiffany Tang (2023) - Clare Boothe Luce Assistant Professor, University of Notre Dame
- Dennis Shen (2023) - Assistant Professor, USC
- Spencer Frei (2023) - Assistant Professor, UC Davis
- Rebecca L. Barter (2022) - Research Assistant Professor, University of Utah
- Luiz Chamon (2022) - Research Group Leader, University of Stuttgart
- Angela Zhou (2022) - Assistant Professor, University of Southern California
- Briton Park (2022) - Citadel Securities
- Chandan Singh (2022) - Microsoft Research
- Keyan Nasseri (2022) - Google
- Wooseok Ha (2022) - AWS
- Yan Shuo Tan (2022) - Assistant Profressor, Department of Statistics and Data Science, National University of Singapore
- Xiao Li (2021) - Voleon
- Raaz Dwivedi (2021) - Postdoctoral scholar, MIT / Harvard
- Yu Wang (2020) - Two Sigma
- Merle Behr (2020) - Scientific Expert, Bayer AG
- Nicholas Altieri (2020) - Genentech
- Yuansi Chen (2019) - Assistant Professor, Department of Statistical Sciences, Duke University
- Karl Kumbier (2019) - Postdoctoral Researcher, UC San Francisco
- Jamie Murdoch (2019) - Co-founder / President, clientelligent.ai
- Soren Kunzel (2019) - Data Scientist, Citadel
- Simon Walter (2019) - Data Scientist, Bridgewater
- Sujayam Saha (2018) - Data Scientist, Google
- Reza Abbasi-Asl (2018) - Scientist, Allen Institute for Brain Science
- Christine Kuang (2017) - Data Scientist, Facebook
- Hanzhong Liu (2016) - Assistant Professor, Department of Statistics, Tsinghua University
- Sumanta Basu (2016) - Assistant Professor, Department of Statistics, Cornell University
- Sivaraman Balakrishnan (2016) - Assistant Professor, Department of Statistics, Carnegie Mellon University
- Adam Bloniarz (2016) - Data Scientist, Google
- Siqi Wu (2016) - Data Scientist, Citadel
- Hongwei Li (2015) - Senior Data Scientist, UBER
- Antony Joseph (2014) - Staff Data Scientist, Walmart eCommerce
- Taesup Moon (2013) - Research Staff Member, Samsung Advanced Institute of Technology
- Yuval Benjamini (2013) - Stein fellow, Statistics department, Stanford University
- Julien Mairal (2012) - Research Scientist, INRIA
- Yueqing Wang (2012) - Research Scientist, Google
- Hau-tieng Wu (2012) - Assistant Professor, Mathematics Department, University of Toronto
- Garvesh Raskutti (2012) - Assistant Professor, Department of Statistics, Univ. Wisconsin-Madison
- Luke W. Miratrix (2012) - Assistant Professor, Department of Statistics, Harvard University
- Harry Kim (2011) - Product Marketing Manager, Google
- Chinghway Lim (2011) - Assistant Professor, Department of Statistics and Applied Probability, National University of Singapore
- Karl Rohe (2011) - Assistant Professor, Department, University of Wisconsin-Madison.
- Kyle Jia (2010) - Assistant Professor, Peking University, China.
- David Purdy (2009) - Data Scientist, Uber
- Pradeep Ravikumar (2009) - Associate Professor, Department of Computer Sciences, University of Texas, Austin.
- Vince Vu (2009) - Assistant Professor, Department of Statistics, The Ohio State University
- Ethan Anderes (2008) - Assistant Professor, Department of Statistics, University of California, Davis
- Guilherme Rocha (2008) - Assistant Professor, Department of Statistics, Indiana University, Bloomington
- Peng Zhao (2006) - CEO of Citadel Securities, Citadel Investment Group in Chicago, IL.
- Nicolai Meinshausen (2006) - Professor, Department of Statistics, ETH Zurich
- Tao Shi (2005) - Quantitative Researcher, Citadel Investment Group in Chicago, IL.
- Gang Liang (2004) - Quantitative Operations Associate, Bank of America
- Rebecka Jörnsten (2000) - Associate Professor, Mathematical Statistics, Chalmers University of Technology
- Grace Chang (2000) - Senior Manager of Product Development, Marketing Dept, MTN Irancell

@@

- Yeshwanth Cherapanamjeri (2023)
- Arman Sabbaghi (2022)
- Yanjun Qi (2020)
- Ezequiel Smucler (2020)
- Laura Reiger (2019)
- Yanyan Lan (2018)
- Yahong Han (2016)
- Thibault Vatter
- Guoqiang Cai
- Trine Abrahamsen
- Xiaoling Lu
- Xiusheng Lu (2014)
- Xiangyu Chang (2012)
- Ling Hong (2012)
- Toshiyasu Matsushima (2012)
- Yanfeng Gu (2012) - Professor of Electronics Engineering, Harbin Institute of Technology
- Hai Zhang (2012)
- Rodolphe Jenatton (2010)
- Kenichi Hayashi (2010)
- Yangbo He (2010)
- Fei Wu (2010)
- Kei Kobayashi (2008)
- Xing Wang (2007)
